---
title: "Examples"
author: "Christopher M"
date: "Tuesday, May 24, 2016"
output: html_document
---

This package was created to provide analysts with functions that are useful relative to the data within the enterpise. 

[changeclass](#changeclass)

[Dummycode](#Dummycode)

[kfold](#kfold)

[imputer](#imputer)

[preprocess](#preprocess)

[SummaryStats](#SummaryStats)

[StaticMissingVars](#StaticMissingVars)

[parallelApply](#parallelApply)

[trim](#trim)


```{r, echo=FALSE}
require(MASS)
for (f in list.files("F:\\R_Project_wec-preprocess\\R\\") ) {
    if(!f %in% c('Model Wrapper.r')){
    source(paste("F:\\R_Project_wec-preprocess\\R\\",f,sep=''))
    }
}
```

#changeclass
### This function was designed to convert variables to their most likely column class.

```{r}
df = data.frame(point1 = rnorm(1000,1,0),point2 = rnorm(1000,1,100),point3 = rnorm(1000,1,100),point4 = rnorm(1000,1,100))
df$point1 = as.character(df$point1)
df$point2 = as.numeric(df$point2)
df$point3 = as.factor(df$point3)
df$point4 = as.character(df$point4)
str(df)
head(df)
```

### Now we can call our changeclass function 
```{r}
df <- changeclass(df)
str(df)
head(df)
```

### If we have less than 100 rows the function will exit 

```{r}
df = data.frame(point1 = rnorm(31,1,0),point2 = rnorm(31,1,100),point3 = rnorm(31,1,100),point4 = rnorm(31,1,100))
df <- changeclass(df)
```

#Dummycode
* There are many functions our there to dummy code but this function is very intuitive and fast enough for datasets < 100 million.
* We can state whether we want to keep or drop our columns that will be dummy coded
```{r}
df = DummyCode(mtcars,c('carb','am'),F)
head(df)
```

```{r}
df = DummyCode(mtcars,c('carb','am'),T)
head(df)
```

#kfold
* Typically we use kfold for partitioning data for cross validating models as well as an index for parallel functions
```{r}
iris = suppressMessages(kfold(iris,3))
table(iris$Species,iris$folds)
```

#imputer
* The imputer accepts a data frame and whichever column needs to be imputed and then you specify between the following: mean,median,regression
* The imputer will output which method was selected along with the method that it believes is best based upon RMSE. 
```{r}
df = Boston
df[,1][c(1,6,8,12,66,77,88,101,303)] <- NA

imputed.df <- impute(df,1,F,F,T)
imputed.df <- impute(df,1,F,T,F)
imputed.df <- impute(df,1,T,F,F)
```


#SummaryStats
* FiveRepresent: This means 5 uniqe values represent x amount of the data in that variable
* Zscore: This is used for outlier detection, I have it set to display a +5 or -5 standard deviations 
* This function also calls the changeclass function
```{r}
data <- suppressMessages(df_stats(Boston))
data 
```

#StaticMissingVars
* This will function do the following
* Drop any column that has more than 75% of its data missing
* Drop any column that is 95% or more static
* Warn you of any column that is 80-94% static

```{r}
df <- data.frame(ID = 1:100,X = rnorm(100),X2 = rnorm(100),X3 = rnorm(100),D3 = 2,Y = rnorm(100),Output = 1,Volume=4)
df[,2][c(1:75)] <- NA
df[,7][c(1:96)] <- 3
df[,5][c(1:85)] <- 3
df <- Static_Missing_Vars(df) 
```

#parallelApply 
* All of the workstations we use have 8 cores. However we set this to use only 5 of the cores 
* This function essentially works as a a wrapper. You impute the dataframe, function, and number of parameters (Currently the limit is two)

```{r,warning=FALSE}
p.func <- function(x){
  if(x > 2){"big"
  }else if(x == 1){"Thats random"
  }else{"Hello"}
}

df <- data.frame(id = rnorm(10000))
df <- suppressMessages(parallelApply(df,1,p.func,1))
table(df$ParRow)

```
 
## Example with two parameters 
```{r,warning=FALSE}
m.func <- function(x,y){
  if(x > 20 & y > 200){"big"
  }else if(x < 20 & y > 188){"Thats random"
  }else{"Hello"}
}

df <- data.frame(id = rnorm(10000,mean = 18,sd = 10),x =rnorm(10000), y = rnorm(10000,mean = 200,sd = 60))
df <- suppressMessages(parallelApply(df,c(1,3),m.func,2))
table(df$ParRow)

```
 
#trim

* we a have a lot of free form text in our contact data with odd spacing

* the function is using the str_trim from stringr along with multiple gsub statements removing whitespace
```{r}
sentence <- "It    is a beautiful    day, let us go to the        park for a    picinic "
trim(sentence)
```


 
 
 
 
 
 