---
title: "Examples"
author: "Christopher M"
date: "Tuesday, May 24, 2016"
output: html_document
---

This package was created to provide analysts with functions that are useful relative to the data within the enterpise. 

[changeclass](#changeclass)
[Dummycode](#Dummycode)
[Kfold](#Kfold)
[preprocess](#preprocess)
[SummaryStats](#SummaryStats)



```{r, echo=FALSE}
for (f in list.files("F:\\R_Project_wec-preprocess\\R\\") ) {
    if(!f %in% c('Model Wrapper.r')){
    source(paste("F:\\R_Project_wec-preprocess\\R\\",f,sep=''))
    }
}
```

#changeclass
### This function was designed to convert variables to their most likely column class.

```{r}
df = data.frame(point1 = rnorm(1000,1,0),point2 = rnorm(1000,1,100),point3 = rnorm(1000,1,100),point4 = rnorm(1000,1,100))
df$point1 = as.character(df$point1)
df$point2 = as.numeric(df$point2)
df$point3 = as.factor(df$point3)
df$point4 = as.character(df$point4)
str(df)
head(df)
```

### Now we can call our changeclass function 
```{r}
df <- changeclass(df)
str(df)
head(df)
```

### If we have less than 100 rows the function will exit 

```{r}
df = data.frame(point1 = rnorm(31,1,0),point2 = rnorm(31,1,100),point3 = rnorm(31,1,100),point4 = rnorm(31,1,100))
df <- changeclass(df)
```

#Dummycode
### There are many functions our there to dummy code but this function is very intuitive and fast enough for datasets < 100 million.

### We can state whether we want to keep or drop our columns that will be dummy coded
```{r}
df = DummyCode(mtcars,c('carb','am'),F)
head(df)
```

```{r}
df = DummyCode(mtcars,c('carb','am'),T)
head(df)
```

#SummaryStats
```{r}
require(MASS)
data <- df_stats(Boston)
data 
```

 